\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 implementation.tex
.

The implementation was prototyped as PWA-Rel,
%an extension to our
%previously mentioned tool S3CAM \cite{zutshi2014multiple}.
OLS regression
routines were used from Scikit-learn~\cite{pedregosa2011scikit}, a
Python module for machine learning. SAL~\cite{SAL-SRI}
with Yices2~\cite{dutertre2014yices} was the model checker and the SMT
solver.

We used S3CAM to discover the abstraction graph $G$, which was then
trimmed of the nodes which did not contribute to the error search
(nodes from which error nodes were not reachable). In our experiments we
used $1$-relational modeling to create the transition system from $G$.
Using SAL, we checked for the given safety property. If a concrete
trace was obtained from the BMC, it was further checked for validity
by simulating using $\simulate$ to see if it was indeed an error
trace.  If not, $100$ samples from its associated abstract state was
sampled to check the presence of a counter-example in it
neighborhood. This can be further extended by obtaining different
discrete sequences or discrete trace sequences from the model checker.

>>>>

The presented technique was prototyped as a tool: PWA-Rel.
We compared it against S3CAM~\cite{zutshi2014multiple} on several academic
benchmarks.

PWA-Rel was implemented in Python. Its different parts comprised of
the (a) abstraction graph generation, (b) regeression analysis and (c)
BMC. S3CAM was used to compute (a). To compute (b), OLS regression
routines were used from Scikit-learn~\cite{pedregosa2011scikit}, a
Python module for machine learning. Finally, the The bounded model
checking (c) was done using the SAL model checker~\cite{SAL-SRI},
which used Yices2~\cite{dutertre2014yices} as the SMT solver. A naive
alternative linear programming (LP) based model checker specific to the PWA
relational abstractions was implemented utilizing PyGLPK.

We used S3CAM to discover the abstraction graph $G$, which was then
filtered to remove the nodes from which error nodes were not
reachable. In our experiments we used $1$-relational modeling to
create the transition system from $G$. Using the BMC, we checked for
the given safety property. If a concrete trace was obtained, it was
further checked for reproducibility by sampling and simulating its `neighborhood' with the
$\simulate$ function. We define `neighborhood' as the abstract states
corresponding to the returned concrete trace. Specifically, $100$
samples were uniformly randomly chosen and simulated and tested for
error traces. This procedure can also be extended to obtaining
different discrete sequences or discrete trace sequences from the
model checker by requesting distinct counter-examples.

% abstract state was sampled to check the presence of a counter-example
% in it neighborhood. This can be further extended by obtaining
% different discrete sequences or discrete trace sequences from the
% model checker.
